The LSST DESC 3x2pt Tomography Optimization Challenge

### 2021-03-03 paper/paper.tex
Added firt pass as NN method

\subsection{ {\sc NeuralNetwork 1} }

\subsection{ {\sc NeuralNetwork 2} }

>>>>

\subsection{ {\sc NeuralNetwork 1 \& 2} }

The {\sc NeuralNetwork} approach combines the two following ideas:
\begin{itemize}
	\item Use a simple neural network to parameterize a bin assignment function $f_\theta$ taking available photometry as the input and returning a bin number. 
	\item Optimize the parameters of $f_\theta$ as to maximize a target score, either the total SNR \autoref{eq:snr}, or the DETF FoM \autoref{eq:fom}.
\end{itemize}
The interest of this approach is that it actually bypasses the need for a photometric redshift estimate in allocating a galaxy to a bin, and directly solves the problem of optimal bin assignment given available photometry, as to maximize the cosmological information.

Details of the particular neural network are mostly irrelevant, the main difficulty in this approach is to be able to compute the back-propagation of gradients through the cosmological loss function as to update the parameters $\theta$ of the bin assignment function. This is was made possible for this challenge by the \texttt{jax-cosmo} library \citep{jax-cosmo}, which allows the computation of both metrics using the JAX automatic differentiation framework \citep{jax2018github}.

In practice, to parameterize $f_\theta$ we use a simple dense neural network, composed of 3 linear layers of size 500 with leaky\_relu activation function and output batch normalization. The last layer of the model is a linear layer with an output size matching the number of bins, and softmax activation. We implement this model using the JAX-based Flax neural network library \citep{flax2020github}.

Training is performed using batches of 5000 galaxies, over 2000 iterations under the ADAM optimizer \citep{adam} with a base learning rate of 0.001. The loss function $\mathcal{L}$ used for training directly derive from the challenge metrics, and constitutes the only difference between the NeuralNetwork 1 \& NeuralNetwork 2 entries:

\begin{itemize}
	\item NeuralNetwork 1: $\mathcal{L}_1 = 1 / S_{FoM}$
	\item NeuralNetwork 2: $\mathcal{L}_2 = - S_{SNR} $
\end{itemize}

%\subsection{ {\sc NeuralNetwork 2} }
